SunPy - Python for Solar Physics

### 2014-01-29 3-4-Helioviewer.tex
removed the first image and listing, and compressed the description of the download_png portion

Listing \ref{code:hv:downloadlatestpng} demonstrates how to download a
PNG image of the latest AIA 304$\,$\AA\ image available on
\url{Helioviewer.org}.

%Stuart: Do we need this listing?? The same points can be made with 14
% schriste - i agree with stuart here, or maybe just don't show the png file
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net.helioviewer import HelioviewerClient
>>> hv = HelioviewerClient()
>>> hv.download_png('2099/01/01', 4.8, "[SDO,AIA,AIA,304,1,100]",
...                 x0=0, y0=0, width=512, height=512)
\end{minted}
\centering\includegraphics[width=0.5\columnwidth]{helioviewer_latest_aia_304}
\caption{Acquisition of a PNG file showing the latest AIA 304\AA\ image 
available at \url{www.helioviewer.org}.}
\label{code:hv:downloadlatestpng}
\end{listing}

The first argument is the requested time of the image.  Helioviewer
selects images closest to the requested time.  In this case, the
requested time is in the future and so Helioviewer will find the most
recent available image.  The second argument refers to the image
resolution in arcseconds per pixel (larger values mean lower
resolution).  The third argument is a comma-delimited string detailing
the requested observatory $\rightarrow$ instrument $\rightarrow$
detector $\rightarrow$ measurement combination.  The final two numbers
in this string are the visibility and the opacity of the this image
layer (1/0 is visible/invisible with opacity in the range
$0\rightarrow100$, with $100$ meaning fully opaque).  The quantities
\texttt{x0} and \texttt{y0} are the $x$ and $y$ centre points about which to centre
the image (measured in helio-projective cartesian co-ordinates) and
the \texttt{width} and \texttt{height} are the pixel values for the
image dimensions.

It should be noted that the filename of the returned file has the date
and time of the requested time, which is not the time of the observation shown 
in the PNG image.  This is because the Helioviewer API request finds images 
closest to the requested time. However, since the user may ask for images from 
multiple sources, and each of them may have a different observation time, it is
unclear which time is the most appropriate to associate with the resultant 
image.  The Helioviewer API therefore does not select between any of the image 
observation times, but instead returns an image filename based on the request 
time, resulting in predictable filenames.
%this seems like a lot of text for a simple issue, i would recommend removing it

The Helioviewer API allows composition and overlay of images from
multiple sources, based on the positioning metadata in the source FITS
file.  SunPy accesses this overlay/composition capability through the
\texttt{download\_png} method of the Helioviewer client.  Listing
\ref{code:hv:overlaid} gives an example of the composition of three
separate images in to a single image.

@@

The principle difference between Listings~\ref{code:hv:overlaid} and 
\ref{code:hv:downloadlatestpng} is in the layer string (the third
argument).  The layer string has three separate comma separated
entries detailing the data source, its visibility and its opacity.
This functionality makes it simple for SunPy users to generate complex
images from multiple, correctly overlaid, image data sources.

>>>>

The Helioviewer API allows composition and overlay of images from
multiple sources, based on the positioning metadata in the source FITS
file.  SunPy accesses this overlay/composition capability through the
\texttt{download\_png} method of the Helioviewer client.  Listing
\ref{code:hv:overlaid} gives an example of the composition of three
separate image layers in to a single image.

@@

The first argument is the requested time of the image.  Helioviewer
selects images closest to the requested time.  In this case, the
requested time is in the future and so Helioviewer will find the most
recent available images from each source.  The second argument refers
to the image resolution in arcseconds per pixel (larger values mean
lower resolution).  The third argument is a comma-delimited string of
the three requested image layers, the details of which are enclosed
in parentheses. The image layers are described using the observatory
$\rightarrow$ instrument $\rightarrow$ detector $\rightarrow$
measurement combination described above, along with the final two
numbers that denote the visibility and the opacity of the image layer
respectively (1/0 is visible/invisible with opacity in the range
$0\rightarrow100$, with $100$ meaning fully opaque).  The quantities
\texttt{x0} and \texttt{y0} are the $x$ and $y$ centre points about
which to centre the image (measured in helio-projective cartesian
co-ordinates) and the \texttt{width} and \texttt{height} are the pixel
values for the image dimensions.

This functionality makes it simple for SunPy users to generate complex
images from multiple, correctly overlaid, image data sources.
